### 2020-05-28 serial.tex
tweak

The time delays between two epidemiological events can be defined either within an infected individual (e.g., incubation period: infection and symptom onset of an individual) or between infected individuals (e.g., serial interval: symptom onsets of an infector and an infectee).
We can further divide these events into \emph{primary} and \emph{secondary} events.
When we measure an epidemiological time delay within an infected individual (e.g., the incubation period), the primary event is the event that usually occurs before the secondary event ---
most epidemiological events that can be observed within an individual have clear direction (e.g., infection to onset of symptoms) but some may not (e.g., onset of infectiousness and onset of symptoms).
When we measure an epidemiological time delay between infected individuals (e.g., the serial interval), 
the primary and secondary events are defined in terms of the direction of transmission:
the primary event refers to the event that occurs in the infector. 
Again, some of these delays are always positive (the infector is always infected before the infectee) and some are not (it is possible for the infectee to develop symptoms before the infector \citep{he2020temporal}).

>>>>

The time delays between two epidemiological events can be defined either within an infected individual (e.g., incubation period: infection and symptom onset of an individual) or between infected individuals (e.g., serial interval: symptom onsets of an infector and an infectee).
We can further divide these events into \emph{primary} and \emph{secondary} events.
When we measure an epidemiological time delay within an infected individual (e.g., the incubation period), the primary event usually occurs before the secondary event ---
most epidemiological events that can be observed within an individual have clear direction (e.g., infection to onset of symptoms) but some may not (e.g., onset of infectiousness and onset of symptoms).
When we measure an epidemiological time delay between infected individuals (e.g., the serial interval), 
the primary and secondary events are defined in terms of the direction of transmission:
the primary event refers to the event that occurs in the infector. 
Again, some of these delays are always positive (the infector is always infected before the infectee) and some are not (it is possible for the infectee to develop symptoms before the infector \citep{he2020temporal}).
